Homework

### 2016-07-03 Macro Impacts.tex
Correction to Shear
Corrections - integral still divergent...

From earlier, we have

@@

-\Sigma_{yy}&=2\mu k_y(k_z A_x-k_x A_z)\,,\\
-\Sigma_{zz}&=2\mu k_z(k_x A_y-k_y A_x)\,,

@@

which becomes

@@

-\Sigma_{yy}&=2\mu k_y\ps{-\f{k_z}{k_x} \p{k_yA_y+k_zA_z}-k_x A_z}\,,\\
-\Sigma_{zz}&=2\mu k_z\ps{k_x A_y+\f{k_y}{k_x} \p{k_yA_y+k_zA_z}}\,,

@@

which simplifies to

@@

-\Sigma_{yy}&=-\f{2\mu k_y}{k_x}\ps{k_y k_z A_y+\p{k_z^2+k_x^2} A_z}\,,\\
-\Sigma_{zz}&=\f{2\mu k_z}{k_x}\ps{\p{k_x^2 + k_y^2}A_y+k_yk_zA_z}\,,

@@

Hence

@@

A_x&=\f1\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
&=\f1\mu\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
&=\f1\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f1\mu\f{\Sigma_{xx}}{2k^2}\,,\\

@@

By symmetry, we have
A_x&=\f1\mu\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f1\mu\f{\Sigma_{xx}}{2k^2}\,,\\
A_y&=\f1\mu\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\f1\mu\f{\Sigma_{yy}}{2k^2}\,,\\
A_z&=\f1\mu\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\f1\mu\f{\Sigma_{zz}}{2k^2}\,.
Observe, in the case that all stresses are equal, we obtain that $A_x=A_y=A_z=0$, as we should.
We now solve for $A_i$ in terms of $\Sigma_{i}$.

@@

U_x&=k_y A_z-k_z A_y\,,\\
&=\f1\mu\f{1}{2k^2k_y^2k_z^2}\ps{-k_z^3\p{-k_y^2\Sigma_{yy}+(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})}+k_y^3\p{(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})-k_z^2\Sigma_{zz}}}\,,\\
&=\f1\mu\f{1}{2k^2k_y^2k_z^2}\ps{k_z^2k_y^2(k_z\Sigma_{yy}-k_y\Sigma_{zz})-k_z^3(k_x^2-k_z^2)(\Sigma_{xx}-\Sigma_{zz})+k_y^3(k_x^2-k_y^2)(\Sigma_{xx}-\Sigma_{yy})}\,,\\
&=\f1\mu\ps{\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})}\,,\\
Just cyclically permute the indices to obtain the expressions for $U_y$ and $U_z$.
\mu U_x&=\f{1}{2k^2}(k_z\Sigma_{yy}-k_y\Sigma_{zz})-\f{k_z(k_x^2-k_z^2)}{2k^2k_y^2}(\Sigma_{xx}-\Sigma_{zz})+\f{k_y(k_x^2-k_y^2)}{2k^2k_z^2}(\Sigma_{xx}-\Sigma_{yy})\,,\\
\mu U_y&=\f{1}{2k^2}(k_x\Sigma_{zz}-k_z\Sigma_{xx})-\f{k_x(k_y^2-k_x^2)}{2k^2k_z^2}(\Sigma_{yy}-\Sigma_{xx})+\f{k_z(k_y^2-k_z^2)}{2k^2k_x^2}(\Sigma_{yy}-\Sigma_{zz})\,,\\
\mu U_z&=\f{1}{2k^2}(k_y\Sigma_{xx}-k_x\Sigma_{yy})-\f{k_y(k_z^2-k_y^2)}{2k^2k_x^2}(\Sigma_{zz}-\Sigma_{yy})+\f{k_x(k_z^2-k_x^2)}{2k^2k_y^2}(\Sigma_{zz}-\Sigma_{xx})\,.

@@

U_x&=\ps{-(k_z+2k_y)k_x^2k_y^2+3k_zk_x^2(k_x^2-k_z^2)}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,,\\
U_y&=\ps{(2k_x+k_z)k_x^2k_y^2-3k_zk_y^2(k_y^2-k_z^2)}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,,\\
U_z&=\ps{(k_x-k_y)k_x^2k_y^2+3(k_x^3-k_y^3)k_z^2+3k_y^5-3k_x^5}\f{1}{4\mu k^2k_x^2k_y^2}\Sigma\,.
The energy of these shear waves is given
E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
&=\rho\int_V\abs{u_t}^2\,,\\
&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
The integral is horribly divergent about the azimuth - there must have been a mistake...
For shocks, check the laser physics book.

>>>>

From earlier

@@

@@

Imposing the Gauge condition,

@@

-\Sigma_{yz}&=\mu\ps{(k_x^2-k_y^2+k_z^2) A_x+2k_xk_y A_y}\,,\\
-\Sigma_{zx}&=\mu\ps{(k_x^2-k_y^2-k_z^2) A_y-2k_x k_y A_x}\,.

@@

Inverting:

@@

A_z=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}

@@

Hence, by symmetry

@@

A_x&=\f{k_y\Sigma_{zx}-k_z\Sigma_{xy}}{\mu k_x k^2}\,,\\
A_y&=\f{k_z\Sigma_{xy}-k_x\Sigma_{yz}}{\mu k_y k^2}\,,\\
A_z&=\f{k_x\Sigma_{yz}-k_y\Sigma_{zx}}{\mu k_z k^2}\,.

@@

@@

U_x&=\f{k_z^2(k_x\Sigma_{yz}-k_z\Sigma_{xy})+k_y^2(k_x\Sigma_{yz}-k_y\Sigma_{zx})}{\mu k_y k_z k^2}\,,\\
U_y&=\f{k_x^2(k_y\Sigma_{zx}-k_x\Sigma_{yz})+k_z^2(k_y\Sigma_{zx}-k_z\Sigma_{xy})}{\mu k_z k_x k^2}\,,\\
U_z&=\f{k_y^2(k_z\Sigma_{xy}-k_y\Sigma_{zx})+k_x^2(k_z\Sigma_{xy}-k_x\Sigma_{yz})}{\mu k_x k_y k^2}\,,

@@

The energy of these shear waves is given
\begin{align}
E&=\f12\int_V\p{\rho\abs{u_t}^2+\mu\abs{\nabla\cdot u}^2}\,,\\
&=\rho\int_V\abs{u_t}^2\,,\\
&=\mu\int_V\int\f{\diff^3 k}{(2\pi)^3}\int\f{\diff^3 k'}{(2\pi)^3}\p{k k'U(\vec k)\bar U(\vec k')}e^{-\I(\vec k\cdot\vec x-i\beta k t)}e^{\I(\vec k'\cdot\vec x-i\beta k' t)}\,,\\
&=\mu\int\f{\diff^3 k}{(2\pi)^3}\p{k^2\abs{U(\vec k)}^2}\,,\\
\end{align}
The integral is horribly divergent about the azimuth - there must have been a mistake...
\\\\
For shocks, check the laser physics book.
